---
title: "SRT411_Assignment2_joychowdhury"
author: "Joy Chowdhury"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Interacting With APIs
The Cymon API provides data about malware, botnets, phishing, spam, and other malicious activity on a daily basis from a large repository of sources.  The data provided by the API is in a JSON schema, with each object such as domain, ip, malware, and url, contains a response class that provides the details and values in a serializer object.  The API is able to analyze if a given domain was created by a human or an algorigthm.  It can also look up details of a domain name such as the created/updated date, sources, ips associated with the domain, and urls associated with the domain. For IPs, the API is able to find the created/updated dates, sources, events, domains, and urls.  Furthermore, the description of an event associated with an IP is also provided.  A malware object associated with an IP contains the hash value, hash type, and events.
The code to get an a JSON format response from the API is
GET https://cymon.io/api/nexus/v1/ip/x.x.x.x/events/?limit=100&offset=400
The limit specifies the number of items to return, while the offset refers to the point where the output should begin in relation to the complete output.
However, the segment of the url after cymon.io can be replaced with other paths to receive a certain kind of data:

##Blacklist:
/api/nexus/v1/blacklist/ip/{tag}/?
/api/nexus/v1/blacklist/domain/{tag}/

##Domain:
/api/nexus/v1/domain/{name}

##IP:
/api/nexus/v1/ip/{addr}/timeline/
/api/nexus/v1/ip/{addr}/urls/

##Malware:
/api/nexus/v1/malware/{hash_value}/events
The data returned can be implemented into R with the json2veris function from the verisr library, and then analyzed graphically using ggplot.

#Analyzing Google.com (8.8.8.8) events with Cymon and R
The code for the plot can be found at https://github.com/jchowdhury4/Assignment2
Downloading and observing event data
```{r, echo=FALSE}
setwd("~/Class Notes and Assignments/SRT411/Assignment2/")
library(jsonlite)
library(dplyr)
library(ggplot2)
cyurl <- "https://cymon.io/api/nexus/v1/ip/8.8.8.8/events/?limit=200"
cyrep <- "cyrep.json"
if (file.access(cyrep)) {
  download.file(cyurl, cyrep)
}
df <- fromJSON(cyrep)
result <- df$results 
head(result)
```

Aggregating data to count number of each type of report
```{r}
countreporttype <- result %>%
  count(tag)
countreporttype <- data.frame(countreporttype)
colnames(countreporttype) <- c("Report Category","Number of Incidents")
countreporttype
```

Graphing aggregated data
```{r}
gg <- ggplot(data = countreporttype, aes(x = countreporttype$`Report Category`, y = countreporttype$'Number of Incidents')) + geom_bar(stat = "identity") + ggtitle("Number of Reports by Category from Google.com (8.8.8.8)")
gg
```
